DeepSched: A Deep Representation Of Scheduling Policies For Heterogeneous Distributed Systems

### 2020-04-10 paper/core/exp_setup.tex
added train/test split note to setup section

\subsection{Datasets}
A database of tasks and resources is adapted from \emph{Dataset for Task scheduling in Cloud using CLoudsim} \cite{px5b-b729-20}. The used database consists of $100000$ training samples represented as a list of tasks requires to be scheduled. Each training sample contains from $486$ to $84654$ tasks, arranged as a \emph{directed acyclic graph} (DAG) to represent the task dependencies and each task has an execution time for each specific processor. Also, the database contains $188$ resource instances (processors), on which the given tasks scheduled. The desired output of such data is to determine, for each task, the optimal processor to run on, the actual start time (AST) and the actual finish time (AFT).

>>>>

\subsection{Datasets}
A database of tasks and resources is adapted from \emph{Dataset for Task scheduling in Cloud using CLoudsim} \cite{px5b-b729-20}. The used database consists of $100000$ samples represented as a list of tasks requires to be scheduled. Each sample contains from $486$ to $84654$ tasks, arranged as a \emph{directed acyclic graph} (DAG) to represent the task dependencies and each task has an execution time for each specific processor. Also, the database contains $188$ resource instances (processors), on which the given tasks scheduled. The desired output of such data is to determine, for each task, the optimal processor to run on, the actual start time (AST) and the actual finish time (AFT).

The provided samples are divided into $90000$ samples for training and validation and $10000$  samples for testing. We maintain diversity in the test data by including different number of tasks in the test samples.
